%% start of file `template.tex'.
% This file was downloaded and modified from OverLeaf.com.
% Uses moderncv.

\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.9, top=.40in, bottom=.30in]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Newman Perry}{Cate}                              % optional, remove / comment the line if not wanted
\phone[mobile]{(803) 509-1073}                   % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{NPCate01@gmail.com}                               % optional, remove / comment the line if not wanted
\social[github]{PerryCate}
%\homepage{www.myname.webs.com}                     % TODO

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-40pt}

\section{Academics}

\cventry{September 2015 -- June 2019}{BSE Computer Science (GPA 3.3, Departmental 3.8)}{Princeton University}{}{}{
\begin{itemize}
    \item[]\begin{itemize}
\item{\textbf{Favorite CS Courses}: Distributed Systems, Functional Programming, InfoSec, Computing and Optimization, Graphics}
\item{\textbf{Entrepreneurship Courses}: Leadership Development for Business, Creativity Innovation and Design, Entrepreneurial Leadership}
\item{\textbf{Course Assistant/Lab TA for}: Operating Systems (Fall 2017, Fall 2018), Networks (Spring 2017)}
\end{itemize}
\end{itemize}
}

\cventry{June 2016 -- August 2016}{Princeton In Beijing Chinese Language Program}{Beijing Normal University}{}{}{}  % arguments 3 to 6 can be left empty

\vspace{-5pt}
\section{Employment} 


\cventry{June 2018 -- August 2018}{Software Developer Intern - Data Orchestration}{1010data}{}{}{
    \begin{itemize} %\itemsep -2pt
    \item[]\begin{itemize} %\itemsep -2pt
		\item Created plugins and new DAG Workflows for Apache Airflow using Flask.
		\item Worked with project shareholders to determine project scope and acquire iterative feedback.
		\item Built comprehensive early-warning system for missing records in data pipeline with Python 3 and Redis, reducing error turnaround from up to 23 hours to no more than 1 hour.
    \end{itemize}
\end{itemize}
}

\cventry{June 2017 -- September 2017}{Production Engineer Intern - Traffic Infrastructure}{Facebook}{}{}{
    \begin{itemize} %\itemsep -2pt
        \item[]\begin{itemize} %\itemsep -2pt
        \item Designed and implemented a full rewrite of Traffic Infrastructure health checking service in Python 3.
        \item Architected extensible framework for realtime monitoring across every cluster in Facebook's internal network across all products.
        \item Replaced some of the oldest and most inflexible infrastructure code in Facebook's codebase, which had existed for longer than 99.5\% of facebook employees had been employed.
    \end{itemize}
    \end{itemize}
}

\cventry{June 2014 -- August 2015}{Software Developer (Full-time during summers, part-time during school year)}{GraySail LLC}{}{}{
    \begin{itemize} %\itemsep -2pt
        \item[]\begin{itemize} %\itemsep -2pt
        \item Worked with a small team developing custom Lab Inspection software for the University of South Carolina, part of 6-year contract.
        \item Used frontend angular.js with asynchronous calls to custom ORM backend written in PHP.
        \item Designed and implemented data model for tracking radiation in research labs on campuses across the state.
        \item Started as a summer internship, was hired afterwards as the company's 5th developer. Worked 15 months until starting college.
    \end{itemize}
    \end{itemize}
}

\vspace{-5pt}
\section{Projects and Leadership}

\cventry{March 2017 -- March 2018}{President}{Princeton ACM (Programming Club)}{}{}{Led programming club in organizing biweekly talks and events, weekly newsletters, and programming competitions. More than doubled regular attendance, increasing maximum turnout from 35 to 80+.}


\cventry{February 2018 -- Present}{Spring Independent Work}{Uniform-Chat-API}{}{}{Developed a Python 3 web server that exposes a single, uniform, RESTful interface to interact with multiple chat services at once. Relied on the Falcon microservices framework. Open-Source launch date set for November 1st.}


\cventry{June 2016 -- October 2017}{Personal Project}{GroupMe-Utils}{}{}{GroupMe API wrapper written in Java. Includes multiple utilities for saving chat data and performing statistical analysis. Replaces several older projects previously written in Python 3.}


\vspace{-5pt}
\section{Skills, Extracurriculars, and Awards}

\textbf{Programming Languages:} Python 3, Elixir, JavaScript, Go, Octave, Java, C, SQL, HTML+CSS, PHP, OCaml, Bash, K

\textbf{Tools:} Linux, Git, Redis, PostgreSQL, MySQL, Airflow, Docker, Pip/Virtualenv, Mercurial, Maven

\textbf{Extracurriculars}: Princeton Autonomous Vehicle Engineering, Lobster Club Improv Comedy, Acapellago a capella
%\item{NavTalent talent network, associate}

\textbf{Awards}:
\begin{itemize}
    \item[]\begin{itemize}

    \item{\textbf{1st Place}: Google Games NYC Spring 2018 and 2016 (did not attend in 2017)}
    \item{\textbf{1st Place}: Jane Street "eth1" Fall 2015}
    \item{\textbf{Eagle Scout}: Led troop in refurbishing collected computers, donated them to Habitat for Humanity}
    \end{itemize}
\end{itemize}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
